% Cross-Modal Depth-IMU Stress Detection
% Suitable for ACM SenSys submission
% Compile with: pdflatex cross_modal_sensys.tex

\documentclass[sigconf,anonymous=false]{acmart}

\usepackage{tikz}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{xcolor}
\usetikzlibrary{arrows.meta,positioning,fit,shapes.geometric,backgrounds,calc}

\begin{document}

% =============================================================================
\section{Cross-Modal Stress Detection from Depth Video}
\label{sec:cross_modal}
% =============================================================================

\subsection{Problem Statement}

Continuous, passive stress monitoring in clinical environments presents a
fundamental sensing trade-off.  Inertial Measurement Unit (IMU) wristbands
offer reliable stress signatures through accelerometer-derived features---our
FLIRT-LIMU baseline achieves a test AUC of $0.89$---yet compliance is
imperfect: patients remove wearables, sensors lose contact, or deployments
simply do not include wearable instrumentation.  Depth cameras, by contrast,
are fixed infrastructure: always present, always recording, and
privacy-preserving (no RGB texture).  However, depth motion signals encode
stress far less directly than wrist acceleration, yielding a standalone
AUC of only $0.64$ under population-normalized inference.

We ask: \emph{given a cohort where both depth video and IMU data are available
during training, can we train a depth-only classifier that approaches IMU-level
performance at deployment, without requiring the IMU sensor?}

Concretely, our setting is a clinical OUD (Opioid Use Disorder) stress study
in which participants performed alternating stress and non-stress tasks while
recorded by a depth camera and a left-wrist accelerometer.
Binary stress labels follow the shared contract:
non-stress $\in \{$\texttt{jelly}, \texttt{count}, \texttt{baseline}$\}$;
stress $\in \{$\texttt{bad}, \texttt{stress}, \texttt{arithmetic},
\texttt{stroop}$\}$.
Windows of 30\,s (15\,s overlap) are extracted from each task segment,
yielding 3,040 paired (depth, IMU) windows across 62 participants.

% =============================================================================
\subsection{Approach: IMU-Guided Depth Representation Learning}
\label{sec:approach}

Our key insight is to treat the trained IMU model as a \emph{frozen teacher}
whose internal representations encode physiologically meaningful stress
patterns.  During training, the depth model is guided to produce
representations that align with those of the IMU teacher in a shared
projection space.  At deployment, the IMU branch is discarded entirely;
only the depth pathway is executed.

\subsubsection{Feature Representations}

\paragraph{Depth modality.}
Each 30\,s window yields $T=75$ depth frames (5\,Hz, 224$\times$224, top-75
entropy-selected from 150 raw frames).  Each frame is encoded by a frozen
DINOv2-ViT-B/16 encoder producing a $D=768$-dimensional embedding, giving a
window representation $\mathbf{X}_d \in \mathbb{R}^{T \times D}$.

\paragraph{IMU modality.}
Each co-registered 30\,s window of 3-axis wrist acceleration is sampled at
64\,Hz.  FLIRT hand-crafted features are computed per window and the
absolute jelly-baseline delta is appended, yielding a 176-dimensional FLIRT
vector.  A temporal context sequence of length $L=12$ is formed by look-back
concatenation within each (participant, task) group, producing
$\mathbf{F}_i \in \mathbb{R}^{L \times 176}$.

\subsubsection{Shared Architecture}

Figure~\ref{fig:pipeline} illustrates the common backbone shared by all
four alignment variants.

\paragraph{Depth TCN encoder $f_\theta$.}
A dilated Temporal Convolutional Network processes $\mathbf{X}_d$ with
learned attention pooling, producing a window-level representation
$\mathbf{r}_d = f_\theta(\mathbf{X}_d) \in \mathbb{R}^{D_\text{TCN}}$.
The encoder is warm-started from the fold-specific standalone depth checkpoint.

\paragraph{Frozen IMU teacher $g_\psi$.}
A LIMU-BERT transformer fine-tuned for stress classification processes
$\mathbf{F}_i$.  The first-token representation
$\mathbf{e}_i = g_\psi(\mathbf{F}_i) \in \mathbb{R}^{72}$
is extracted as the teacher embedding; all parameters $\psi$ are frozen.

\paragraph{Per-modality input projections.}
Two linear layers $h_d$, $h_i$ map each modality to a shared dimension $D_s$:
\begin{equation}
  \tilde{\mathbf{r}}_d = h_d(\mathbf{r}_d),\quad
  \tilde{\mathbf{e}}_i = h_i(\mathbf{e}_i),\quad
  h_d,h_i : \mathbb{R}^{\cdot}\to\mathbb{R}^{D_s}.
  \label{eq:proj}
\end{equation}

\paragraph{Shared MLP $\phi_\xi$.}
The \emph{same} MLP (LayerNorm $\to$ GELU $\to$ Linear) processes both
modalities, enforcing a common representational geometry:
\begin{equation}
  \mathbf{z}_d = \phi_\xi(\tilde{\mathbf{r}}_d),\quad
  \mathbf{z}_i = \phi_\xi(\tilde{\mathbf{e}}_i).
  \label{eq:shared}
\end{equation}

\paragraph{Stress classifier $c_\omega$.}
A two-layer MLP (LayerNorm $\to$ Linear $\to$ GELU $\to$ Dropout $\to$ Linear)
maps $\mathbf{z}_d$ to binary stress logits.
Stress probability is $p = \mathrm{softmax}(c_\omega(\mathbf{z}_d))_1$.

\subsubsection{Alignment Objective Variants}

All variants share the same classification loss on the depth path:
\begin{equation}
  \mathcal{L}_\text{cls} = \text{CE}(c_\omega(\mathbf{z}_d),\, y).
  \label{eq:cls}
\end{equation}
They differ in how the IMU teacher supervises the shared space.

\paragraph{V1 --- Cosine alignment.}
Pulls the depth and IMU shared representations together via cosine
dissimilarity, providing a point-wise geometric constraint:
\begin{equation}
  \mathcal{L} = \mathcal{L}_\text{cls}
              + \lambda_a\underbrace{\!\left(1
              - \tfrac{\mathbf{z}_d\cdot\mathbf{z}_i}
                      {\|\mathbf{z}_d\|\|\mathbf{z}_i\|}\right)
              }_{\mathcal{L}_\text{cosine}}.
  \label{eq:v1}
\end{equation}
The IMU path is fully frozen; gradients flow only through the depth branch.

\paragraph{V2 --- Gradient Reversal Layer (GRL).}
Replaces the point-wise constraint with an adversarial distributional
alignment.  A modality discriminator $D_\eta$ (2-layer MLP) tries to
classify whether a shared vector originates from the depth or IMU path.
A Gradient Reversal Layer inverts the gradient sign with scale $\alpha$
during backpropagation, forcing the depth encoder to confuse the
discriminator while the discriminator trains normally:
\begin{equation}
  \mathcal{L} = \mathcal{L}_\text{cls}
              + \underbrace{\text{CE}(D_\eta(\mathbf{z}_\text{all}),
                            \mathbf{d}_\text{all})
              }_{\mathcal{L}_\text{domain}},
  \label{eq:v2}
\end{equation}
where $\mathbf{z}_\text{all} = [\text{GRL}_\alpha(\mathbf{z}_d);\,
\mathbf{z}_i^{\text{sg}}]$ concatenates GRL-wrapped depth and
stop-gradient IMU representations, and $\mathbf{d}_\text{all}$ are the
corresponding modality labels $\{0,1\}$.
At training equilibrium, the discriminator is forced to chance accuracy,
indicating that depth representations are distributionally indistinguishable
from IMU representations.  $D_\eta$ is discarded at inference.

\paragraph{V3 --- KL logit consistency.}
Rather than aligning embedding distributions, V3 directly aligns the
\emph{stress predictions} of both modalities in the shared classification
space.  The shared classifier $c_\omega$ is applied to both $\mathbf{z}_d$
and $\mathbf{z}_i$.  The IMU projection ($h_i$, $\phi_\xi$) is \emph{not
frozen}---it receives its own classification loss $\mathcal{L}_\text{cls}^{(i)}$
so that $c_\omega(\mathbf{z}_i)$ produces meaningful stress predictions before
serving as the KL target.  The depth path is then trained to match those
predictions:
\begin{equation}
  \mathcal{L} = \mathcal{L}_\text{cls}^{(d)}
              + \mathcal{L}_\text{cls}^{(i)}
              + \lambda_\text{kl}\,T^2\underbrace{
              \mathrm{KL}\!\left(
                \sigma\!\!\left(\tfrac{c_\omega(\mathbf{z}_i)^\text{sg}}{T}\right)
                \,\Big\|\,
                \sigma\!\!\left(\tfrac{c_\omega(\mathbf{z}_d)}{T}\right)
              \right)}_{\mathcal{L}_\text{KL}},
  \label{eq:v3}
\end{equation}
where $(\cdot)^\text{sg}$ denotes stop-gradient and $T$ is a temperature
hyperparameter tuned by Optuna.
The $T^2$ factor preserves gradient magnitude~\cite{hinton2015distilling}.
The KL term trains only the depth path; $\mathcal{L}_\text{cls}^{(i)}$
trains only the IMU projection independently.

\paragraph{V4 --- Joint fine-tuning.}
Extends V3 by adding an explicit pre-shared alignment term.
Both IMU and depth projection paths are trained (as in V3), but V4
additionally pulls the \emph{intermediate} representations together
before they enter the shared MLP.
First, an MSE loss directly aligns the pre-shared projections, pulling
both paths toward a common intermediate representation:
\begin{equation}
  \mathcal{L}_\text{mse} = \|\tilde{\mathbf{r}}_d - \tilde{\mathbf{e}}_i\|_2^2.
  \label{eq:mse}
\end{equation}
Second, the IMU path receives its own classification supervision, ensuring
that the unfrozen IMU projection maps to a stress-discriminative region of
the shared space:
\begin{equation}
  \mathcal{L}_\text{cls}^{(i)} = \text{CE}(c_\omega(\mathbf{z}_i),\, y).
  \label{eq:cls_imu}
\end{equation}
The combined loss is:
\begin{equation}
  \mathcal{L} = \mathcal{L}_\text{cls}
              + \lambda_i\,\mathcal{L}_\text{cls}^{(i)}
              + \lambda_m\,\mathcal{L}_\text{mse}
              + \lambda_\text{kl}\,T^2\,\mathcal{L}_\text{KL},
  \label{eq:v4}
\end{equation}
where $\mathcal{L}_\text{KL}$ uses $c_\omega(\mathbf{z}_i)$ detached as
the target, training only the depth path for this term.

\paragraph{V5 --- GRL adversarial + KL logit consistency.}
V2 acts in the shared \emph{embedding} space; V3 acts in the
\emph{prediction} space.  V5 applies both simultaneously, exerting
alignment pressure at two complementary levels of the pipeline:
\begin{equation}
  \mathcal{L} = \mathcal{L}_\text{cls}^{(d)}
              + \mathcal{L}_\text{cls}^{(i)}
              + \underbrace{\mathcal{L}_\text{domain}}_{\text{embedding}}
              + \lambda_\text{kl}\,T^2\,
                \underbrace{\mathcal{L}_\text{KL}}_{\text{predictions}},
  \label{eq:v5}
\end{equation}
where $\mathcal{L}_\text{domain}$ is the GRL adversarial term from
Eq.~\eqref{eq:v2} and $\mathcal{L}_\text{KL}$ is the temperature-scaled
KL term from Eq.~\eqref{eq:v3}.
The GRL forces $\mathbf{z}_d$ to be distributionally indistinguishable
from $\mathbf{z}_i$ in the shared space, while the KL additionally
constrains the stress probability distributions produced by the shared
classifier to agree between modalities.
The discriminator $D_\eta$ is discarded at inference.
The hypothesis is that neither embedding alignment nor prediction
alignment alone is sufficient; constraining both levels jointly may
remove residual misalignment that each single objective leaves behind.

\subsubsection{Inference}

All variants share the same depth-only inference path.  Subject-normalised
embeddings $\tilde{\mathbf{X}}_d^{(s)}$ (z-scored per test participant $s$
from their own windows) are passed through the depth branch:
\begin{equation}
  \hat{y} = \arg\max\; c_\omega\!\left(
    \phi_\xi\!\left(h_d\!\left(f_\theta\!\left(
      \tilde{\mathbf{X}}_d^{(s)}\right)\right)\right)\right).
  \label{eq:infer}
\end{equation}
The IMU teacher $g_\psi$, projections $h_i$, and any alignment components
(discriminator, KL targets) are discarded entirely.

% =============================================================================
\subsection{Experimental Setup}
\label{sec:eval}

\paragraph{Evaluation protocol.}
Participant-disjoint folds via GroupKFold($n=5$) grouped by
\texttt{base\_subject\_id}, with inner validation via
GroupShuffleSplit(test\_size$=0.2$, seed$=42+\text{fold}$).
Hyperparameters are tuned by Optuna (50 trials) on fold 1 and applied to
all 5 folds.  The decision threshold is swept across 19 values on the
validation set and applied unchanged to the test set.
All cross-modal variants use subject-normalised inference at val and test time.

\paragraph{Metrics.}
AUC (ROC), Balanced Accuracy (BA), Sensitivity, Specificity, and MCC,
averaged across folds.  AUC is the primary metric (threshold-free).

% =============================================================================
\subsection{Pipeline Diagram}
\label{sec:diagram}

\begin{figure*}[t]
\centering
\begin{tikzpicture}[
  >=Stealth, font=\small,
  box/.style={rectangle, rounded corners=3pt, draw, thick,
    minimum width=2.0cm, minimum height=0.65cm, text centered, inner sep=3pt},
  frozen/.style    ={box, fill=blue!10,   draw=blue!50!black},
  trainable/.style ={box, fill=orange!15, draw=orange!60!black},
  shared/.style    ={box, fill=green!15,  draw=green!50!black},
  loss/.style      ={box, fill=red!10,    draw=red!50!black,
                     minimum width=1.6cm, minimum height=0.6cm},
  variant/.style   ={rectangle, rounded corners=4pt, draw, thick,
                     inner sep=6pt, minimum width=3.6cm},
  arrow/.style     ={->, thick},
  darrow/.style    ={->, thick, blue!60!black, dashed},
  lbl/.style       ={font=\scriptsize\itshape, text=gray},
]

% =====================================================================
% SHARED BACKBONE
% =====================================================================

% Depth path (orange, left)
\node[trainable] (frames) at (0, 0)
  {DINOv2 frames\\$\mathbf{X}_d \!\in\! \mathbb{R}^{75\times768}$};
\node[trainable] (tcn)    at (0,-1.5)
  {TCN $f_\theta$\\(warm-start)};
\node[trainable] (hd)     at (0,-3.0)
  {Proj.\ $h_d$\\$D_\text{TCN}\!\to\! D_s$};

% IMU teacher path (blue, right)
\node[frozen] (limu)  at (7.5, 0)
  {LIMU-BERT $g_\psi$\\(frozen teacher)};
\node[frozen] (ei)    at (7.5,-1.5)
  {$\mathbf{e}_i \!\in\! \mathbb{R}^{72}$};
\node[frozen] (hi)    at (7.5,-3.0)
  {Proj.\ $h_i$\\$72\!\to\! D_s$};

\node[lbl] at (7.5, 0.65)
  {\textit{IMU branch: training only, discarded at inference}};

% Pre-shared labels
\node[lbl] at (0.3,-3.85)   {$\tilde{\mathbf{r}}_d$};
\node[lbl] at (7.2,-3.85)   {$\tilde{\mathbf{e}}_i$};

% Shared MLP (center)
\node[shared] (shared) at (3.75,-5.2)
  {Shared MLP $\phi_\xi$\quad\textit{(same weights both modalities)}};

% z_d, z_i
\node[trainable] (zd) at (1.5,-6.7) {$\mathbf{z}_d\!\in\!\mathbb{R}^{D_s}$};
\node[frozen]    (zi) at (6.0,-6.7) {$\mathbf{z}_i\!\in\!\mathbb{R}^{D_s}$};

% Classifier → logits
\node[trainable] (cls)    at (1.5,-8.0)  {Classifier $c_\omega$};
\node[trainable] (logitsd) at (1.5,-9.2) {logits$_d$};
\node            (logitsi) at (6.0,-9.2) {logits$_i = c_\omega(\mathbf{z}_i)$};

% Backbone arrows
\draw[arrow, orange!70!black] (frames) -- (tcn);
\draw[arrow, orange!70!black] (tcn)    -- (hd);
\draw[arrow, orange!70!black] (hd)     -- (shared -| hd)
    node[midway, left, lbl]{};
\draw[darrow]                 (limu)   -- (ei);
\draw[darrow]                 (ei)     -- (hi);
\draw[darrow]                 (hi)     -- (shared -| hi);

\draw[arrow]  (shared) -- (zd)    node[midway, left,  lbl]{depth};
\draw[arrow]  (shared) -- (zi)    node[midway, right, lbl]{IMU};
\draw[arrow]  (zd)     -- (cls);
\draw[arrow]  (cls)    -- (logitsd);
\draw[arrow, dashed, gray!60] (zi) -- (logitsi)
    node[midway, right, lbl]{V3, V4, V5};

% Background panels
\begin{scope}[on background layer]
  \node[fill=orange!5, rounded corners=5pt,
        fit=(frames)(tcn)(hd), inner sep=5pt] {};
  \node[fill=blue!5,   rounded corners=5pt,
        fit=(limu)(ei)(hi), inner sep=5pt] {};
\end{scope}

% Divider line
\draw[gray!50, thick, dashed]
  (-1.8,-10.4) -- (9.8,-10.4)
  node[midway, above, font=\scriptsize\bfseries, text=gray!80]
  {Alignment objectives (training only)};

% =====================================================================
% VARIANT PANELS  (2 × 2 grid below backbone)
% =====================================================================

% --- V1: Cosine ---------------------------------------------------
\begin{scope}[shift={(-1.3,-12.0)}]
  \node[variant, fill=orange!5, draw=orange!60!black, minimum height=2.6cm]
    (v1box) at (1.5, -0.8) {};
  \node[font=\small\bfseries, text=orange!70!black] at (1.5, 0)
    {V1 — Cosine Alignment};
  \node[loss, fill=orange!10] (lcosine) at (1.5, -0.9)
    {$\mathcal{L}_\text{cos}=1-\cos(\mathbf{z}_d,\mathbf{z}_i)$};
  \node[font=\scriptsize, align=center] at (1.5,-1.9)
    {Point-wise geometric\\constraint in $\mathbb{R}^{D_s}$};
\end{scope}

% --- V2: GRL -------------------------------------------------------
\begin{scope}[shift={(3.5,-12.0)}]
  \node[variant, fill=purple!5, draw=purple!50!black, minimum height=2.6cm]
    (v2box) at (1.5, -0.8) {};
  \node[font=\small\bfseries, text=purple!70!black] at (1.5, 0)
    {V2 — GRL Adversarial};
  \node[loss, fill=purple!10, draw=purple!40!black] (lgrl) at (1.5, -0.7)
    {$\text{GRL}_\alpha(\mathbf{z}_d)\!\to\!D_\eta$};
  \node[loss, fill=purple!10, draw=purple!40!black] at (1.5,-1.6)
    {$\mathcal{L}_\text{domain}=\text{CE}(D_\eta,\mathbf{d})$};
  \node[font=\scriptsize, align=center] at (1.5,-2.35)
    {Adversarial: depth enc.\\confuses discriminator};
\end{scope}

% --- V3: KL Logits -------------------------------------------------
\begin{scope}[shift={(8.3,-12.0)}]
  \node[variant, fill=teal!5, draw=teal!50!black, minimum height=2.6cm]
    (v3box) at (1.5,-0.8) {};
  \node[font=\small\bfseries, text=teal!70!black] at (1.5, 0)
    {V3 — KL Logit Consistency};
  \node[loss, fill=teal!10, draw=teal!40!black] (lkl) at (1.5, -0.7)
    {$\mathcal{L}_\text{KL}=T^2\,\mathrm{KL}(p_i\,\|\,p_d)$};
  \node[font=\scriptsize, align=center] at (1.5,-1.6)
    {$p_d=\sigma(c_\omega(\mathbf{z}_d)/T)$\\$p_i=\sigma(c_\omega(\mathbf{z}_i)/T)^\dagger$};
  \node[font=\scriptsize, align=center] at (1.5,-2.35)
    {Align stress predictions\\in classification space};
\end{scope}

% --- V4: Joint Fine-tuning ----------------------------------------
\begin{scope}[shift={(-1.3,-16.0)}]
  \node[variant, fill=cyan!5, draw=cyan!50!black, minimum height=3.4cm]
    (v4box) at (1.5,-1.2) {};
  \node[font=\small\bfseries, text=cyan!70!black] at (1.5, 0)
    {V4 — Joint Fine-tuning};
  \node[loss, fill=cyan!10, draw=cyan!40!black] at (1.5,-0.75)
    {$\mathcal{L}_\text{cls}^{(i)}=\text{CE}(c_\omega(\mathbf{z}_i), y)$};
  \node[loss, fill=cyan!10, draw=cyan!40!black] at (1.5,-1.65)
    {$\mathcal{L}_\text{mse}=\|\tilde{\mathbf{r}}_d-\tilde{\mathbf{e}}_i\|^2$};
  \node[loss, fill=cyan!10, draw=cyan!40!black] at (1.5,-2.55)
    {$\lambda_\text{kl}\,T^2\,\mathrm{KL}(p_i^\dagger \| p_d)$};
  \node[font=\scriptsize, align=center] at (1.5,-3.3)
    {Unfreezes $h_i$, $\phi_\xi$; both paths\\jointly supervised};
\end{scope}

% --- V5: GRL + KL --------------------------------------------------
\begin{scope}[shift={(8.3,-16.0)}]
  \node[variant, fill=violet!5, draw=violet!50!black, minimum height=3.4cm]
    (v5box) at (1.5,-1.2) {};
  \node[font=\small\bfseries, text=violet!70!black] at (1.5, 0)
    {V5 — GRL + KL};
  \node[loss, fill=violet!10, draw=violet!40!black] at (1.5,-0.6)
    {$\text{GRL}_\alpha(\mathbf{z}_d)\!\to\!D_\eta\;\Rightarrow\;\mathcal{L}_\text{domain}$};
  \node[loss, fill=violet!10, draw=violet!40!black] at (1.5,-1.65)
    {$\lambda_\text{kl}\,T^2\,\mathrm{KL}(p_i^\dagger\,\|\,p_d)$};
  \node[font=\scriptsize, align=center] at (1.5,-2.65)
    {Embedding \emph{and} prediction\\alignment simultaneously};
\end{scope}

% --- Shared total loss label ------------------------------------
\node[font=\scriptsize, align=left, text=gray] at (-1.3,-19.8) {
  $^\dagger$ IMU logits detached for KL term (depth is student)
};

% =====================================================================
% INFERENCE PATH
% =====================================================================
\node[box, fill=gray!10, draw=gray!50, minimum width=11.0cm,
      font=\small] (infer) at (3.75,-20.5)
  {$\hat{y}=\arg\max\; c_\omega\!\left(
      \phi_\xi\!\left(h_d\!\left(f_\theta\!\left(
      \tilde{\mathbf{X}}_d^{(s)}\right)\right)\right)\right)$\quad
   \textbf{Depth-only inference} (IMU branch discarded)};

% =====================================================================
% LEGEND
% =====================================================================
\begin{scope}[shift={(9.0,-13.2)}]
  \node[trainable, minimum width=1.6cm, minimum height=0.4cm, font=\scriptsize]
    at (0, 0) {Trainable};
  \node[frozen,    minimum width=1.6cm, minimum height=0.4cm, font=\scriptsize]
    at (0,-0.7) {Frozen};
  \node[shared,    minimum width=1.6cm, minimum height=0.4cm, font=\scriptsize]
    at (0,-1.4) {Shared weights};
  \node[loss,      minimum width=1.6cm, minimum height=0.4cm, font=\scriptsize]
    at (0,-2.1) {Loss term};
  \draw[arrow, orange!70!black] (-0.9,-2.9)--(-0.3,-2.9)
    node[right, font=\scriptsize]{Grad.\ flows};
  \draw[darrow] (-0.9,-3.5)--(-0.3,-3.5)
    node[right, font=\scriptsize]{No gradient};
\end{scope}

\end{tikzpicture}
\caption{
  \textbf{Cross-modal depth-IMU training pipeline and alignment variants.}
  \textit{Top}: The shared backbone processes depth DINOv2 frame embeddings
  through a warm-started TCN encoder and per-modality input projections into a
  shared MLP (identical weights for both modalities).
  The frozen LIMU-BERT teacher contributes IMU embeddings during training only.
  \textit{Middle}: Four alignment variants attach to different points of the
  shared backbone.
  \textbf{V1} (cosine) applies a point-wise geometric constraint between
  $\mathbf{z}_d$ and $\mathbf{z}_i$.
  \textbf{V2} (GRL) uses an adversarial discriminator with gradient
  reversal to enforce distributional alignment.
  \textbf{V3} (KL) aligns the stress prediction distributions of both
  paths in the shared classification space.
  \textbf{V4} (joint) additionally unfreezes the IMU projection path,
  adds MSE on pre-shared representations, and provides the IMU path its
  own classification loss.
  \textbf{V5} (GRL+KL) combines V2 and V3, applying adversarial
  embedding alignment and KL prediction alignment simultaneously.
  \textit{Bottom}: At inference, all variants reduce to an identical
  depth-only forward pass with subject-normalised inputs.
}
\label{fig:pipeline}
\end{figure*}

% =============================================================================
\subsection{Results}
\label{sec:results}

Table~\ref{tab:results} compares all cross-modal variants against standalone
depth and IMU baselines under the same participant-disjoint evaluation
protocol (5-fold GroupKFold, thresholds swept on held-out validation BA).
All cross-modal models use subject-normalised inference; the IMU branch is
discarded at test time.

\begin{table}[h]
\centering
\caption{Test-set performance (mean $\pm$ std across 5 participant-disjoint folds).
BA = balanced accuracy, Sens.\ = sensitivity, Spec.\ = specificity.
$\dagger$ = pending full 5-fold evaluation.
Dash (--) indicates metric not available for that baseline.}
\label{tab:results}
\small
\begin{tabular}{lccccc}
\toprule
\textbf{Model} & \textbf{AUC} & \textbf{BA} & \textbf{Sens.} & \textbf{Spec.} & \textbf{MCC} \\
\midrule
\multicolumn{6}{l}{\textit{IMU baselines (upper bound, requires wearable)}} \\
FLIRT-LSTM        & 0.890 & 0.822 & -- & -- & -- \\
FLIRT-LIMU-BERT   & 0.863 & 0.784 & -- & -- & -- \\
\midrule
\multicolumn{6}{l}{\textit{Depth-only (no wearable at inference)}} \\
Pop.\ norm  & 0.638\,$\pm$\,0.054 & 0.587\,$\pm$\,0.032
            & -- & -- & 0.173\,$\pm$\,0.069 \\
Subj.\ norm & \textbf{0.717}\,$\pm$\,0.037 & 0.636\,$\pm$\,0.011
            & -- & -- & 0.262\,$\pm$\,0.050 \\
\midrule
\multicolumn{6}{l}{\textit{Cross-modal (IMU guidance, depth-only inference)}} \\
V1: Cosine
  & 0.702\,$\pm$\,0.071 & \textbf{0.643}\,$\pm$\,0.050
  & 0.696\,$\pm$\,0.079 & 0.590\,$\pm$\,0.129 & 0.249\,$\pm$\,0.084 \\
V2: GRL
  & 0.688\,$\pm$\,0.029 & \textbf{0.643}\,$\pm$\,0.036
  & 0.669\,$\pm$\,0.130 & 0.617\,$\pm$\,0.193 & 0.250\,$\pm$\,0.053 \\
V3: KL logits$^\dagger$  & -- & -- & -- & -- & -- \\
V4: Joint$^\dagger$      & -- & -- & -- & -- & -- \\
V5: GRL + KL$^\dagger$   & -- & -- & -- & -- & -- \\
\bottomrule
\end{tabular}
\end{table}

Both evaluated cross-modal variants (V1, V2) improve over the
population-normalised depth baseline ($\text{AUC}=0.638$) by $+10.0\%$
and $+7.8\%$ respectively, while neither yet surpasses the subject-normalised
depth baseline ($\text{AUC}=0.717$).

The two completed variants reveal a key trade-off.  Cosine alignment (V1)
achieves higher mean AUC ($0.702$) but with substantially higher variance
($\pm0.071$ vs.\ $\pm0.029$), indicating sensitivity to fold-specific subject
composition.  The GRL variant (V2) produces more balanced sensitivity/specificity
($0.669$\,/\,$0.617$ vs.\ $0.696$\,/\,$0.590$ for V1), consistent with
adversarial alignment encouraging distributional rather than point-wise matching.  Both variants
achieve nearly identical balanced accuracy ($0.643$) and MCC ($\approx 0.250$).

The three pending variants address the core limitation identified in V1 and V2:
embedding-space alignment does not directly supervise the stress-discriminative
subspace.  V3 closes this gap by aligning \emph{classification distributions}
rather than embedding vectors.  V4 further adds pre-shared MSE alignment,
providing the tightest geometric constraint across the full projection path.
V5 tests the orthogonal hypothesis: rather than deepening alignment at one
level, it applies adversarial embedding alignment (V2) and prediction
alignment (V3) simultaneously.  If the two objectives are complementary,
V5 should outperform both; if they conflict or share the same information,
performance should be similar to the better of V2 and V3.

\end{document}
